A Framework for Discrete Change

### 2008-11-12 papers/individual/individual.tex
Updated authors in individual paper
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/depmix@240 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/depmix@241 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass[a4paper,12pt,man]{apa} % nobf, doc, apa

@@

\author{Ingmar Visser \& Maarten Speekenbrink}

@@

The Weather Prediction Task (WPT, Knowlton, Squire \& Gluck, 1994) is
a probabilistic categorization task in which participants learn to
predict (or categorize) the state of the weather (sun or rain) on the
basis of four ``tarot'' cards (cards with abstract geometrical
patterns).  On a given trial, one, two, or three cues are present.
There are a total of 14 possible cue patterns, and each one is
associated with a particular probability distribution over the states
of the weather.  In order to perform in the task, participants must
predict the weather in accordance with these conditional
probabilities.

@@

Alternative non-strategy based analyses of the WPT
\cite{Lagnado??,Speekenbrink??} have estimated response strategies by
logistic regression, allowing the regression coefficients to change
over time.

%associative, rule-based.
Here, we analyze the behavior of a single individual performing the
WPT for 200 trials.  We chose to analyse the ``average'' participant
(the participant with performance closest to the group average) in a
large unpublished dataset.  We let each state be characterized by a
GLM with a Binomial distributed response and logistic link function
(i.e., a logistic regression model).  We are particularly interested
in evidence for strategy switching and whether a DMM can recover a
strategy model in line with \cite{Gluck2002}.

>>>>

\documentclass[a4paper,12pt,man,english]{apa} % nobf, doc, apa

\usepackage[english]{babel} % ik krijg anders foute citaties...in Zweeds formaat???

@@

\author{Ingmar Visser, Brenda R. J. Jansen, \& Maarten Speekenbrink}

@@

The Weather Prediction Task \cite<WPT>{Knowlton1994} %(WPT, Knowlton, Squire \& Gluck, 1994) 
is
a probabilistic categorization task in which participants learn to
predict (or categorize) the state of the weather (sun or rain) on the
basis of four ``tarot'' cards (cards with abstract geometrical
patterns).  On a given trial, one, two, or three cues are present.
There are a total of 14 possible cue patterns, and each one is
associated with a particular probability distribution over the states
of the weather.  In order to perform in the task, participants must
predict the weather in accordance with these conditional
probabilities.

@@

Alternative non-strategy based analyses of the WPT
\cite{Lagnado2006,Speekenbrink2008} have estimated response strategies by
logistic regression, allowing the regression coefficients to change
over time.

%associative, rule-based.
Here, we analyze the behavior of a single individual performing the
WPT for 200 trials.  We chose to analyse the ``average'' participant
(the participant with performance closest to the group average) in a
large unpublished dataset.  We let each state be characterized by a
GLM with a Binomial distributed response and logistic link function
(i.e., a logistic regression model).  We are particularly interested
in evidence for strategy switching and whether a DMM can recover a
strategy model in line with \citeA{Gluck2002}.
